\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-01 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%\usepackage{cases}
%% or use the graphicx package for more complicated commands
\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
\usepackage{epsfig}
\usepackage{subfig}
\usepackage{comment}

@@

\begin{figure}[h]
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilties K  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=3000  
}
}     
\caption{........}
\label{fem_cv_represent_a}
\end{figure}

\medskip
In this section three different sets of simulations were explained. Starting from an initial square set-up to validate the existance of cross flow and how the simulator works, we moved to a larger domain by increasing the aspect ratio. The reason was to give more time, space and greater number of elements to our simulator and again see how the front/cross-flow will develop. The third test-case is based in the initial and boundary condition of the second set of simulations. Now we would like to know what is the impact of different mobility ratios (see Fig.\ref{fig:1testcase}) and how the cross-flow as well as the simulation will progress on time. The purpose of these three cases was to verify that our model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.

\begin{figure}[h]
\makebox[\textwidth]{%
\subfigure[MR1]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}%
}%
\hfill    
\subfigure[MR10]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR1]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}%
}%
\hfill    
\subfigure[MR10]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR1]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf}%
}%
\hfill    
\subfigure[MR10]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf}%
}}%
\caption{Comparing MR1 and MR10 cases using fixed mesh using the same map of permeabilities as test-case in Fig.\ref{fig:testcase}. Simulation time step increases from top to bottom and from (a,b) t=100(start) to (e,f) t=3000(end).}
\label{fig:1testcase}
\end{figure}

>>>>

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%\usepackage{cases}
%% or use the graphicx package for more complicated commands
\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
\usepackage{epsfig}
%\usepackage{subfig}
\usepackage{comment}

@@

\begin{figure}[h]
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilties K  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=3000  
}
}     
\caption{Using unstructured but fixed mesh the domain is devide into $4$ different regions of different permeabilities as these are represented in the figures above}
\label{fem_cv_represent_a}
\end{figure}

\medskip
In this section three different sets of simulations were explained. Starting from an initial square set-up to validate the existance of cross flow and how the simulator works, we moved to a larger domain by increasing the aspect ratio. The reason was to give more time, space and greater number of elements to our simulator and again see how the front/cross-flow will develop. The third test-case is based in the initial and boundary condition of the second set of simulations. Now we would like to know what is the impact of different mobility ratios (see Fig.\ref{fig:6a},\ref{fig:6b},\ref{fig:6c}) and how the cross-flow as well as the simulation will progress on time. The purpose of these three cases was to verify that our model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.

\begin{figure}[h]
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR1 at t = 100 (start)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 at t = 100 (start)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
\label{fig:6a}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR1 at t = 1500 (middle)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 at t = 1500 (middle)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
\label{fig:6b}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR1 at t = 3000 (end)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 at t = 3000 (end)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
\label{fig:6c}
\end{figure}
